---
title: "Getting Started with R"
author: "Nicholas Jacob"
date: "1/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Keybrdg_LS_Removed_Redundant_Rows <- read.csv("/cloud/project/Keybrdg_LS_Removed_Redundant_Rows.csv", header=FALSE)
```

## R Markdown

Here is what I know!  You need to click in environment and import the data set.  Here I have imported ``Keybrdg_LS_Removed_Redundant_Rows"  Next I will start to use that data.  So here I am with the summary statistics

```{r baf}
summary(Keybrdg_LS_Removed_Redundant_Rows)
```

## Submitting to GitHub

To submit the changes you made to github you are going to need to let RStudio know who you are.  In the terminal below run the following commands

git config --global user.name "User Name Here"
git config --global user.email "email@ecok.edu"

After you have done this click the Git tab on the upper right hand side and you can push (or commit) your code.  Make sure to select the items and add a note otherwise it won't go through.

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
