---
title: "Getting Started with R"
author: "Nicholas Jacob"
date: "1/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl) 
Keybrdg_LS_Removed_Redundant_Rows <- read.csv("/cloud/project/Data/Keybrdg_LS_Removed_Redundant_Rows.csv", header=FALSE)
Q1 <- read_excel("Data/LegalShieldQ1.xlsx", sheet = 1, skip = 0)
```

## R Markdown

Here is what I know!  You need to click in environment and import the data set.  Here I have imported ``Keybrdg_LS_Removed_Redundant_Rows"  Next I will start to use that data.  So here I am with the summary statistics

```{r baf}
summary(Keybrdg_LS_Removed_Redundant_Rows)
summary(Q1)

```

## Submitting to GitHub

To submit the changes you made to github you are going to need to let RStudio know who you are.  In the terminal below run the following commands

git config --global user.name "User Name Here"
git config --global user.email "email@ecok.edu"

After you have done this click the Git tab on the upper right hand side and you can push (or commit) your code.  Make sure to select the items and add a note otherwise it won't go through.


## Using R

Let's see if I can use R to extract some information from the file.  I am looking at "DESCRIPTION 1" column here

```{r}
n = nrow(Keybrdg_LS_Removed_Redundant_Rows["V3"])
table(Keybrdg_LS_Removed_Redundant_Rows['V3'])
cbind(table(Keybrdg_LS_Removed_Redundant_Rows['V3'])/n)
```

```{r Pivot Table (State x Product)}
library(pivottabler)
pt <- PivotTable$new()
pt$addData(Keybrdg_LS_Removed_Redundant_Rows)
pt$addColumnDataGroups("V3")
pt$addRowDataGroups("V2")
pt$defineCalculation(calculationName="Claims by State", summariseExpression="n()")
pt$renderPivot() 
```
```{r Linear Model}
lmTotalSpendSales =  lm(Q1$totally~Q1$TotalX)
lmLglSpendSales = lm(Q1$Legal...5~Q1$`Total LGL`)
lmBusSpendSales = lm(Q1$BUS...13~Q1$`Total BUS`)
lmLchSpendSales = lm(Q1$Launch...17~Q1$`Total LCH`)
lmEspSpendSales = lm(Q1$`LS En Espanol...21`~Q1$`Total Legal Espanol`)
lmIdsSpendSales = lm(Q1$SAIDT~Q1$`Total IDS`)
lmMultiVariateSpendSales = lm(Q1$totally~Q1$`Total LGL` + Q1$`Total BUS` + Q1$`Total IDS` + Q1$`Total LCH` + Q1$`Total Legal Espanol` + Q1$TotalX)
plot(lmTotalSpendSales, pch = 16, col = "red")
summary(lmTotalSpendSales)
summary(lmLglSpendSales)
summary(lmBusSpendSales)
summary(lmLchSpendSales)
summary(lmEspSpendSales)
summary(lmIdsSpendSales)
summary(lmMultiVariateSpendSales)

```

```{r}
plot(lmTotalSpendSales)
abline(lmSpendSales, col="blue") #Create the linear regression
```

See I did more this weekend... 
